Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-16 paper/paper.tex

\begin{proof}
  If no partition of \TAlg's components exists, then it simply ends the phase and performs no re-partition, thus the cost is $0$.
  Hence, in the following we bound the cost of moving to a component-respecting partition.

@@

    Consider a request $(u, v)$ that triggered the r-epartitiong and let $U, V$ be clusters of these nodes.
    Note that $U\neq V$, as otherwise such a request would not trigger a reconfiguration.
    We consider cases upon types of clusters $U$ and $V$.
    Note that this is impossible that either $U$ or $V$ is of type $C_3$, as otherwise we encounter a component of size $4$ and this would contradict the case assumption that the component-respecting partition exists.
    If either $U$ or $V$ is of type $C_1$, then this cluster can fit the merged component, and the rebalance is local within $U$ and $V$, for the cost of at most $3$ migrations.

>>>>

\begin{proof}
  Observe that when the repartition is triggered by \TAlg, the resulting partition is component-respecting.
  Otherwise, if it does not exist, \TAlg simply ends the phase and performs no repartition.

@@

    Consider a request between $u$ and $v$ that triggered the repartition and let $U$ and $V$ be their respective clusters.
    Note that $U\neq V$, as otherwise the request would not trigger a~reconfiguration.
    We consider cases upon types of clusters $U$ and $V$.
    Note that this is impossible that either $U$ or $V$ is of type $C_3$, as otherwise we merge components of size $3$, and no component-respecting partition exists, a contradiction.
    If either $U$ or $V$ is of type $C_1$, then this cluster can fit the merged component, and the rebalance is local within $U$ and $V$, for the cost of at most $3$ migrations.
